# Results
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(ggalluvial)
library(RColorBrewer)
library(vcd)
library(ggmosaic)
options(dplyr.summarise.inform = FALSE)

cab = read.csv("cab.csv")
cab = cab %>% mutate(Strata = factor(Strata)) %>% mutate(Strata = fct_recode(Strata, "Over 65" = "66 to Max", "Under 40" = "0 to 40"))
```


```{r}
cab_counts = cab %>% filter(!(Strata %in% c('Under 40', 'Uninsured', 'Native', 'Others', 'Pacific'))) %>% filter(!(complication %in% c('Deep Sternal Infection', 'Reintervention for Myocardial Ischemia'))) %>% arrange(Year, complication)
```



# Question 1: Does our data change over time in terms of frequency of complications, readmissions, and demographics/medical information?
```{r}
complication_counts = cab_counts %>% group_by(Year, complication) %>% summarise(Freq=sum(Count)) %>% arrange(Year, desc(Freq)) %>% mutate(complication=factor(complication, levels = unique(complication)))
readmission_counts = cab_counts %>% group_by(Year, readmission) %>% summarise(Freq=sum(Count))
strata_counts = cab_counts %>% group_by(Year, category, Strata) %>% summarise(Freq=sum(Count)) %>% subset(category != "All") 
```

```{r}
ggplot(complication_counts, aes(x=Year, y=Freq, fill=complication)) +
  geom_bar(stat='identity', position='dodge') +
  scale_fill_brewer(palette="Dark2") +
  labs(title="Counts of Complications over the Years", y="Count")
ggplot(complication_counts, aes(x=Year, y=log10(Freq), fill=complication)) +
  geom_bar(stat='identity', position='dodge') +
  scale_fill_brewer(palette="Dark2") +
  labs(title="Log Counts of Complications over the Years", y="Log Count")
```

```{r}
ggplot(readmission_counts, aes(x=Year, y=Freq, fill=readmission)) +
  geom_bar(stat='identity', position='dodge') +
  scale_fill_brewer(palette="Dark2") +
  labs(title="Counts of Readmissions over the Years", y="Count")
```

```{r fig.height=6, fig.weight=6}
for (c in unique(strata_counts$category)) {
  if (c == "Age"){
    print(ggplot(strata_counts %>% subset(category == c), aes(x=Year, y=Freq, fill=Strata)) +
      geom_bar(stat='identity', position='dodge') +
      scale_fill_brewer(c, palette="Dark2") +
      labs(title=paste(paste("Counts of", c), "over the Years"), y="Count") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)))
  }else{
    print(ggplot(strata_counts %>% subset(category == c) %>% arrange(Year, desc(Freq)) %>% mutate(Strata = factor(Strata, levels=unique(Strata))), aes(x=Year, y=Freq, fill=Strata)) +
      geom_bar(stat='identity', position='dodge') +
      scale_fill_brewer(c, palette="Dark2") +
      labs(title=paste(paste("Counts of", c), "over the Years"), y="Count") +
      theme(axis.text.x = element_text(angle = 45, hjust = 1)))
  }
}
```

# Question 2: What are the most common complications associated with CABG?
```{r}
ggplot(complication_counts %>% group_by(Year, complication) %>% summarize(Freq=sum(Freq)) %>% mutate(complication=factor(complication)), aes(x=complication, y=Freq, fill=complication)) +
  geom_bar(stat="identity") +
  facet_wrap(~ Year, scales = "free") +
  labs(x="Complication", y="Count", title="Counts for Complications") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Question 3: What complications most often lead to readmission to the hospital?
```{r fig.height=4, fig.width=6}
df=cab_counts %>% subset(category=="All")

df$Year <- as.factor(df$Year)

# Plotting a grouped bar chart
ggplot(df, aes(x = complication, y = Yes, fill = readmission)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ Year, scales = "free") +
  labs(x = "Complication", y = "Count", fill = "Readmission") +
  ggtitle("Complication Readmission Rates") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


# Question 4: Does your demographic data and medical information impact your likelihood to face a complication from a CABG procedure?
```{r}
age_counts = cab_counts %>% subset(category == "Age") %>% group_by(complication, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Age = Strata) %>% mutate(Age=factor(Age)) %>% uncount(weights = Freq)
cabg_counts = cab_counts %>% subset(category == "CABG type") %>% group_by(complication, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, CABG.Type = Strata) %>% mutate(CABG.Type=factor(CABG.Type)) %>% uncount(weights = Freq)
gender_counts = cab_counts %>% subset(category == "Gender") %>% group_by(complication, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Gender = Strata) %>% mutate(Gender=factor(Gender)) %>% uncount(weights = Freq)
pay_counts = cab_counts %>% subset(category == "PayorType") %>% group_by(complication, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, "Payment Type" = Strata) %>% mutate("Payment Type"=factor("Payment Type")) %>% uncount(weights = Freq)
race_counts = cab_counts %>% subset(category == "Race") %>% group_by(complication, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Race = Strata) %>% mutate(Race=factor(Race)) %>% uncount(weights = Freq)
```

```{r}
ggplot(age_counts) +
  geom_mosaic(aes(x=product(Age), fill = Complication)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1), aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())
```

```{r}
ggplot(cabg_counts) +
  geom_mosaic(aes(x=product(CABG.Type), fill = Complication)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1), aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())
```

```{r}
ggplot(gender_counts) +
  geom_mosaic(aes(x=product(Gender), fill = Complication)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1), aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())
```


# Question 5: Does your demographic data and medical information impact your likelihood that you will be readmitted to the hospital regardless of complication?
```{r}
age_read_counts = cab_counts %>% subset(category == "Age") %>% group_by(readmission, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Readmission = readmission, Age = Strata) %>% mutate(Age=factor(Age)) %>% uncount(weights = Freq)

ggplot(age_read_counts) +
  geom_mosaic(aes(x=product(Readmission, Age), fill = Readmission)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust=1), aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())
```

```{r fig.height=6, fig.width=6}
age_read_mosaic = cab_counts %>% subset(category == "Age") %>% group_by(complication, readmission, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Readmission = readmission, Age = Strata) %>% mutate(Age=factor(Age))
age_read_mosaic

vcd::mosaic(Readmission ~ Complication + Age, data = age_read_mosaic)

```


# Question 6: Does your demographic data, medical information, and complication impact your likelihood that you will be readmitted to the hospital?
```{r fig.height=6}
age_comp_read_counts = cab_counts %>% subset(category == "Age") %>% group_by(complication, readmission, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Readmission = readmission, Age = Strata) %>% mutate(Age=factor(Age)) %>% uncount(weights = Freq)
cabg_comp_read_counts = cab_counts %>% subset(category == "CABG type") %>% group_by(complication, readmission, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Readmission = readmission, CABG.Type = Strata) %>% mutate(CABG.Type=factor(CABG.Type)) %>% uncount(weights = Freq)
gender_comp_read_counts = cab_counts %>% subset(category == "Gender") %>% group_by(complication, readmission, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Readmission = readmission, Gender = Strata) %>% mutate(Gender=factor(Gender)) %>% uncount(weights = Freq)
pay_comp_read_counts = cab_counts %>% subset(category == "PayorType") %>% group_by(complication, readmission, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Readmission = readmission, PayorType = Strata) %>% mutate(PayorType=factor(PayorType)) %>% uncount(weights = Freq)
race_comp_read_counts = cab_counts %>% subset(category == "Race") %>% group_by(complication, readmission, Strata) %>% summarize(Freq = sum(Count)) %>% rename(Complication = complication, Readmission = readmission, Race = Strata) %>% mutate(Race=factor(Race)) %>% uncount(weights = Freq)

ggplot(age_comp_read_counts) +
  geom_mosaic(aes(x=product(Readmission, Age), fill = Readmission)) +
  facet_wrap(~Complication) +
  labs(title = "Mosaic Plots of Age and Readmission for Each Complication") +
  theme(aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())

cat("----- Age -----\n")
for (complication in unique(age_comp_read_counts$Complication)){
cat(paste(complication, "\n"))
test = chisq.test(table(age_comp_read_counts$Readmission, age_comp_read_counts$Age, age_comp_read_counts$Complication)[, , complication])
cat(paste(paste("Chi Squared Statistic:", round(test$statistic, 4))), "\n")
cat(paste(paste("p-value:", round(test$p.value, 4))), "\n")
cat(paste("-----------------", "\n"))
}

ggplot(cabg_comp_read_counts) +
  geom_mosaic(aes(x=product(Readmission, CABG.Type), fill = Readmission)) +
  facet_wrap(~Complication) +
  labs(title = "Mosaic Plots of CABG Type and Readmission for Each Complication") +
  theme(axis.text.x = element_text(angle = 45, hjust=1), aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())

cat("----- CABG Type -----\n")
for (complication in unique(cabg_comp_read_counts$Complication)){
cat(paste(complication, "\n"))
test = chisq.test(table(cabg_comp_read_counts$Readmission, cabg_comp_read_counts$CABG.Type, cabg_comp_read_counts$Complication)[, , complication])
cat(paste(paste("Chi Squared Statistic:", round(test$statistic, 4))), "\n")
cat(paste(paste("p-value:", round(test$p.value, 4))), "\n")
cat(paste("-----------------", "\n"))
}

ggplot(gender_comp_read_counts) +
  geom_mosaic(aes(x=product(Readmission, Gender), fill = Readmission)) +
  facet_wrap(~Complication) +
  labs(title = "Mosaic Plots of Gender and Readmission for Each Complication") +
  theme(aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())

cat("----- Gender -----\n")
for (complication in unique(gender_comp_read_counts$Complication)){
cat(paste(complication, "\n"))
test = chisq.test(table(gender_comp_read_counts$Readmission, gender_comp_read_counts$Gender, gender_comp_read_counts$Complication)[, , complication])
cat(paste(paste("Chi Squared Statistic:", round(test$statistic, 4))), "\n")
cat(paste(paste("p-value:", round(test$p.value, 4))), "\n")
cat(paste("-----------------", "\n"))
}

ggplot(pay_comp_read_counts) +
  geom_mosaic(aes(x=product(Readmission, PayorType), fill = Readmission)) +
  facet_wrap(~Complication) +
  labs(title = "Mosaic Plots of Insurance Type and Readmission for Each Complication") +
  theme(axis.text.x = element_text(angle = 45, hjust=1), aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())

cat("----- Insurance Type -----\n")
for (complication in unique(pay_comp_read_counts$Complication)){
cat(paste(complication, "\n"))
test = chisq.test(table(pay_comp_read_counts$Readmission, pay_comp_read_counts$PayorType, pay_comp_read_counts$Complication)[, , complication])
cat(paste(paste("Chi Squared Statistic:", round(test$statistic, 4))), "\n")
cat(paste(paste("p-value:", round(test$p.value, 4))), "\n")
cat(paste("-----------------", "\n"))
}

ggplot(race_comp_read_counts) +
  geom_mosaic(aes(x=product(Readmission, Race), fill = Readmission)) +
  facet_wrap(~Complication) +
  labs(title = "Mosaic Plots of Race and Readmission for Each Complication") +
  theme(axis.text.x = element_text(angle = 45), aspect.ratio = 1, axis.ticks.x=element_blank(), line = element_blank(), axis.ticks.y=element_blank())

cat("----- Race -----\n")
for (complication in unique(race_comp_read_counts$Complication)){
cat(paste(complication, "\n"))
test = chisq.test(table(race_comp_read_counts$Readmission, race_comp_read_counts$Race, race_comp_read_counts$Complication)[, , complication])
cat(paste(paste("Chi Squared Statistic:", round(test$statistic, 4))), "\n")
cat(paste(paste("p-value:", round(test$p.value, 4))), "\n")
cat(paste("-----------------", "\n"))
}
```





